Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-03-03 main.tex
update acknowledgements
merge two results sections

\section{Results}
\subsection{Model Sizes}
By default, I use 40k parameters for i6 features compared to 4M for \wvtwo.
Can we improve the performance by making the model larger?
\subsubsection{wav2vec 2.0 Components}
To understand where \wvtwo uses the parameters and how much they contribute to the \gls{FE}'s performance, we run it with different configurations.
The results for different widths and depths are shown in \refTab{table:features_w2v_size}.
% Kernel sizes and strides were chosen as (10, 3, 3, 3, 3, 2), (5, 2, 2, 2, 2, 2) for 6 layers, (10, 6, 3, 3, 3), (5, 4, 2, 2, 2) for 5 layers, (10, 6, 6, 3), (5, 4, 4, 2) for 4 layers, (20, 6, 6), (10, 4, 4) for 3 layers, (32, 20), (16, 10) for 2 layers and (320), (160) for 1 layer.
While a larger inner dimension leads to a better performance, no major effect can be observed regarding the number of layers.
The final projection additionally improves the performance, see \refTab{table:features_w2v_proj}.
We can additionally vary the kernel size and final norm.

\subsubsection{Inner Dimensions}
As a larger inner dimension clearly showed better performance for the \wvtwo \gls{FE}, we increase the inner dimensions of the i6 features as well.
However, as shown in \refTab{table:features_i6_size}, neither increasing the inner dimension of the first layer nor the second layer helps to improve the performance.

\subsubsection{First Layer Window Size}
What role does the size of the first layer play? Is it important to cover one pitch period (max. fundamental period)?
By default, I use a window size of \ms{16}.
Experiments on using different window sizes in \refTab{table:features_window_size} suggest that a larger window size has a detrimental effect while going from the default \ms{16} down to \ms{10} shows a marginal improvement.

@@

\subsection{Model Sizes}
Results are in the following tables.
\input{tables/features_w2v_size}
\input{tables/features_w2v_proj}
\input{tables/features_i6_size}
\input{tables/features_window_size}

@@

\ifinterspeechfinal
     Personal information revealing author identity
\else
     Anonymized information not revealing author identity
\fi

>>>>

@@

\subsection{Model Sizes}
By default, I use 40k parameters for i6 features compared to 4M for \wvtwo.
Can we improve the performance by making the model larger?

\subsubsection{wav2vec 2.0 Components}
To understand where \wvtwo uses the parameters and how much they contribute to the \gls{FE}'s performance, we run it with different configurations.
The results for different widths and depths are shown in \refTab{table:features_w2v_size}.
% Kernel sizes and strides were chosen as (10, 3, 3, 3, 3, 2), (5, 2, 2, 2, 2, 2) for 6 layers, (10, 6, 3, 3, 3), (5, 4, 2, 2, 2) for 5 layers, (10, 6, 6, 3), (5, 4, 4, 2) for 4 layers, (20, 6, 6), (10, 4, 4) for 3 layers, (32, 20), (16, 10) for 2 layers and (320), (160) for 1 layer.
While a larger inner dimension leads to a better performance, no major effect can be observed regarding the number of layers.
The final projection additionally improves the performance, see \refTab{table:features_w2v_proj}.
We can additionally vary the kernel size and final norm.
\input{tables/features_w2v_size}
\input{tables/features_w2v_proj}

\subsubsection{Inner Dimensions}
As a larger inner dimension clearly showed better performance for the \wvtwo \gls{FE}, we increase the inner dimensions of the i6 features as well.
However, as shown in \refTab{table:features_i6_size}, neither increasing the inner dimension of the first layer nor the second layer helps to improve the performance.
\input{tables/features_i6_size}

\subsubsection{First Layer Window Size}
What role does the size of the first layer play? Is it important to cover one pitch period (max. fundamental period)?
By default, I use a window size of \ms{16}.
Experiments on using different window sizes in \refTab{table:features_window_size} suggest that a larger window size has a detrimental effect while going from the default \ms{16} down to \ms{10} shows a marginal improvement.
\input{tables/features_window_size}

@@

\ifinterspeechfinal
     The authors would like to thank Wei Zhou for providing the baseline \gls{CTC} model.
\else
     The acknowledgements would likely reveal the author identity and are therefore hidden for the double-blind review process.
\fi
